\chapter{Introduction}
\label{chap:intro}

The volume of shipping traffic is increasing rapidly. One of the side effects of this growth is that the number of ships in transit becomes larger. This increases the chances of infractions at sea like environmentally devastating ship accidents, piracy, illegal fishing, drug trafficking, and illegal cargo movement. This has compelled many organizations, from environmental protection agencies to insurance companies and national government authorities, to have a closer watch over the open seas. One of the active companies in this field is airbus. Airbus offers comprehensive maritime monitoring services by building a meaningful solution for wide coverage, fine details, intensive monitoring, premium reactivity and interpretation response. Combining its proprietary-data with highly-trained analysts, they help to support the maritime industry to increase knowledge, anticipate threats, trigger alerts, and improve efficiency at sea.
A lot of work has been done over the last 10 years to automatically extract objects from satellite images with significative results but no effective operational effects. Recently, Airbus has turned to Kagglers to increase the accuracy and speed of automatic ship detection\cite{challintro}. 

\section{Motivation}
\label{sec:motivation}

As it was mentioned in previous section, increasing the accuracy and speed of automatic ship detection is the aim of this challenge. To overcome this task, we decided to try the tools, which are widely utilized in this field. This brought us to Mask R-CNN and U-net. U-Net was originally developed for the biomedical data but has just demonstrated itself as liable for satellite images also. Mask R-CNN framework is an extended version of Faster R-CNN which was also an improvement to Fast R-CNN. The Mask Region-based Convolutional Neural Network has proven to be robust and performant in surmounting the image segmentation difficulties\cite{HeGDG17}. The complexity and results of Mask R-CNN has motivated us to study it further and utilized it for this project. The Mask R-CNN outputs bounding boxes and masks of the detected objects which are quite what we are seeking in the proposed challenge, to detect ships in an image and extract their masks. 






